 \begin{document}
\maketitle 
\begin{Summaryns. The human gene is affected by the energy frequencies, and thus leading to certain genetic modifications, so that the individual organism acquires certain genetic traits, which occur through the genetic interaction (between the husband, wife and their children), according to mutual processes dependent on the dominant and the recessif.
The evolution of the human being came in according to the processes of endogenous, and through that the source of human is one. 
Therefore, the evolution of natural selection is the presence of genetic characteristics unique to a particular group of one species, without the other, which emerge according to the biological clock to sync with the future time; according to the periodicity of past time, which has an impact on the physiology and attributes of the individual genetic.
This genetic differentiation appears in the ability of individual's senses to develop into a higher stage, such as the ability to sense the future, reading ideas, their limited reproduction, and other paranormal, as well as the difficulty of social integration of this group with another group; because of the difficulty of interaction between their genomes with the environment, and so on.
In addition, the female came through the process of endogenous from male cells. Interpretation of the process of human reproduction according to a genetic logarithm, and how evolution evolved in the budding of Eve and all human offspring from one source. Thus, the energy of the self gives the sperm that the characteristic of buoyancy due to the specific genetic charge and density, and therefore the determination of the sexual of the fetus depends on the formation of special charge.\end{summary}
 
\section{Introduction}
When one of the children was infected with respiratory infection, he had a strange behavior, during awake and sleeping, so he acted as if the ghost was chasing him and sometimes screaming for fear of a frightening vision of dreams, which turned out to be the same dreams that his father had in the past, unlike the rest of his brothers . This is a motive for the search for the history of his predecessors, where I found that one of his parents had suffered from the same symptoms at some point in the past. There were also some behavioral traits in the male child, who was born before the female child who had visual symptoms. As if the genetic traits passed from parents to children in a time sequence and based on positioning. Both children's grandparents did not have these traits. Are these neurological processes that have occurred to some children related to the development of their nerves in the future, and at the same time is considered a genetic advantage, as well as some characterized by the continuous speech during anger, whether it speaks on its own or that the phenomenon occurs compulsively caused by anger and inherited by some individuals. In addition, the emergence of some racist behaviors between religions, such as the claim of each religion to the degree of preference to others, according to the natural selection as well as beliefs about the creation of human beings, so all the above has been a catalyst for research and to know the truth of those matters.
Why do people make revolutionary changes such as wars and scientific revolutions only in certain stages?
Is it possible that successive genetic processes occur to produce genetic traits from non-parents?
Can we avoid the downside of future events?
How was the human being synthesized, and why did he die?
What are the stages of evolution of the visual and auditory systems in the human body?
Where did the female come from?
Are there genetic indications that humans can live again after they die?
 
\subsection{Hypothesis} 
1.Adam came from a genetically modified clay strain that contained unique EVE as a genetic code and then evolved into a sperm that passed to the offspring, and therefore this viral microstructure has the potential to mutate into other organisms, and to develop its senses.
2. Eve came from up stem cell of Adam's body by endopolygeny, and therefore the synthesis structure of the organism is responsible for determining its behavior and its traits, and therefore differences arise between nature and nurture.
3. Every organism contains a solid totipotent stem cell that retains his embryonic cloned, in a state of dormancy, and activates after death in a pre-determined period, and therefore the organisms return to life after death by endogenous process.
4. There are time-waves that contain codes of acquired genetic traits of the ancestors, which emerge periodically, as common traits if any organisms acquired them will become inherited in their offspring, and therefore the future time was written beforetime.
5. Changes in the genetic characteristics of successive generations occur during the emergence of certain genetic traits that have been previously introduced within the human DNA to adapt to the environment, and therefore the determinants of natural selection remain in dormancy until they are stimulated.
6. Both human reproduction and sexual determination depend on exponential function, and therefore every person has a half-life, according to the exponential decay.
 
\section{Methods}
Inductive method, based on observation, experimentation and conclusion, by examining the behavior of individuals for a long time and the mechanism of their awareness as well as genetic diseases that arise in children, although not familiar with those events, which was in the era of parents. As well as the assumptions to solve some genetic issues, especially the theory of evolution developed by Darwin.
 
\section{Acquire genetic traits by interaction}

Some genetic traits acquired into the embryo (in the initial stages of formation) have been added, which are likely to appear at some stage as a result of a particular arousal, and may acquire hereditary traits during his lifetime. The creature benefits from these genetic traits as a means of survival and adaptation, etc. These genetic traits are either structural or change in structure only in terms of height, shortness and width (no change in the DNA chain) or axioms, which are found in different proportions among humans such as science and disease, so-called differentiation between creatures. Some creatures have specific genetic traits that are included in the coding of the gene and then move to the offspring, while others do not acquire it. Through the structure of the formation in the form of entanglement ring, so the structure of the creature (animal or human) may be prolonged or shrinking due to daily practices, and due to adaptation to environmental conditions, but did not come as a result of evolution from one creature to another, as it was claimed that “humans came from the monkey”. This is due to the denatured which altered the sequence of human DNA and then was distilled into the monkey. Finally, if genetic change occurs in parents, will become a genetic trait that acquired by their children. “STEC belonging to serogroups O26,O103, and O111 were characterized to determine clonality and to profile virulence traits”/citep(<cite class="Itx_cote" data-bib-text="@articale{Schmidt, Herbert, et al. 1999,
Doi= {https://doi.org/10.1086/314537},
Url = {https://academic.oup.com/jid/article/179/1/115/877122/Non-O157-H7-Pathogenic-Shiga-Toxin-Producing},
Year = {1999},
month = {January},
Publisher = {JID},
Volume = {179},
Number = {1},
Pages = {115--123},
Author = {Schmidt, H., Geitz, C., Tarr, P. I., Frosch, M., & Karch, H},
Title = {Non-O157: H7 pathogenic Shiga toxin-producing Escherichia coli: phenotypic and genetic profiling of virulence traits and evidence for clonality},
Journal = {Journal of infectious diseases}" data-bib-key="Schmidt, Herbert. et al. 1999" contenteditable="false"><a href="#Schmidt_Herbert_et_al_1999"></a></cite>). The individual also acquires genetic traits through mutual influence. Thus, when a person contacts friends who use drugs, his behavior is affected by the passing of a response to quantum emissions from their hearts, which receive a response from his heart, and then become part from his genome, and therefore plays a guiding and stimulating role in directs that individual to take drugs and so on. Genetic traits have been previously programmed, to appear periodically, and are suitable for the future as well as showing the traits of the effects were appeared in the past to come back and affect the behavior of humans in the presently or future, and recognize this during the similarity of the results, that led to those behaviors. “The D allele of the ACE gene is equally prevalent among African Americans and whites and may be related to venous thrombosis among African-American men”\citep(<cite class="Itx_cote" data-bib-text="@articale{Dilley, Anne, et al. (1998),
Doi= {{10.1093/oxfordjournals.aje.a009363},
Url = { + http://dx.doi.org/10.1093/oxfordjournals.aje.a009363},
Year = {1998},
Month = {January},
Publisher = {Oxford Journal},
Volume = {147},
Number = {1},
Pages = {30--35},
Author = {Dilley, Anne and Austin, Harland and Hooper, W. Craig and Lally, Cathy and Ribeiro, J. A. and Wenger, Nanette Kass and Rawlins, Peggy and Evatt, Bruce},
Title = {Relation of three genetic traits to venous thrombosis in an African-American population},
Journal = {American journal of epidemiology}" data-bib-key="Dilley, Anne, et al. 1998" 
contenteditable="false"><a href="#Dilley_Anne_et_al_1998">Dilley, Anne, et al.1998</a></cite>). Thus, inherited traits that affect the lifes of individuals, either as a means of survival and facilitating the affairs of life, or a familiarity that brings unhappiness and misery. Therefore, the emergence of such genetic traits is subject to several factors, according to the individual's own decision, because s/he has the ability to choose, regardless some traits have already been added by God, as well as genetic traits that maintain offspring (the structure and sequence of DNA of organisms), which no organ can modify or delete it. “Epistasis—nonlinear genetic interactions between polymorphic loci—is the genetic basis of canalization and speciation, and epistatic interactions can be used to infer genetic networks affecting quantitative traits”\citep(<cite class="Itx_cote" data-bib-text="@articale{Huang, Wen, et al. 2012),
Doi= {10.1073/pnas.1213423109},
Url = {https://doi.org/10.1073/pnas.cm10313},
Year = {2012},
Month = {September},
Publisher = {PANS},
Volume = {109},
Number = {38},
Pages = {15553--15559},
Author = {Wen Huanga,
Stephen Richardsb,
Mary Anna Carbonea,
Dianhui Zhub,
Robert R. H. Anholtc,
Julien F. Ayrolesa,
Laura Duncana,
Katherine W. Jordana,
Faye Lawrencea,
Michael M. Magwirea,
Crystal B. Warnerb,
Kerstin Blankenburgb,
Yi Hanb,
Mehwish Javaidb,
Joy Jayaseelanb,
Shalini N. Jhangianib,
Donna Muznyb,
Fiona Ongerib,
Lora Peralesb,
Yuan-Qing Wub,
Yiqing Zhangb,
Xiaoyan Zoub,
Eric A. Stonea,
Richard A. Gibbsb, and
Trudy F. C. Mackaya},
Title = {Epistasis dominates the genetic architecture of Drosophila quantitative traits},
Journal = {Proceedings of the National Academy of Sciences}" data-bib-key="Huang, Wen, et al 2012" 
contenteditable="false"><a href="#Huang_Wen_et_al_2012">Huang, Wen, et al. 2012</a></cite>). Thus, interactions occur during a fracture structure coupled with an acoustic fingerprint that plays a role in genetic modification, and then to become as acquired genetic trait.
 
\section{Conclusions}
Chromosomes are linked together according to the similarity of quantum accumulation between their genome, and therefore, chromosomal disintegration may occur due to the genome variation of tow chromatids, that were identical in interstitial phase.
Also, both the couple's chromatids (men and women), which are linked according to quanta similarity between their genetic material, may be separated due to the separation of one chromatid from the other, and thus the family disintegrates. Furthermore, both husband and wife are as a linkage chromosome, which consists of two chromatids, that are identical in the genetic material (which appears as an affinity between them). Therefore, the coupling genes of our DNA have been timed in the past.
Gravity is therefore the ability to form an associative affinity through quantitative cognition between two objects to make a identical ratios between their different genetic material. It is also a branch of stereochemistry, especially isomerism, and therefore it takes a certain isomer structure due to the mechanism of interconnections between the objects. Which means the forces of time influence between objects.
Thus, the force of gravitational are also exchanged between two identical objects, where the first part leaves quantities of the gravitation, and a similar quantities of the gravitation is left by the second body. The first part relates to the location of the second part on the second body, and the second is related to the first place. As a result, there is a mutual effect between two objects. Moreover, the gravitational does not depend on mass, but rather on the quantum accumulation of the genetic material.
In addition, heart's optional electromagnetism in which double-polar quantum magnets direct their magnetic field toward a specific external magnetic field. Moreover, the direction of the magnetic field depends on the field strength of an internal quantum magnet — not on the strength of the external magnetic field. While less quantities oriented towards the external magnetic field — the higher quantities are shown as contrast and opposite direction of that external magnetic field, and so on. That is, the field of heart's magnetic changes due to the direction of the higher cumulative quantum field of intrenal-magnets, which changes its direction towards a vector that opposes the external magnetic field. Moreover, the heart has opposite internal magnets, that depending on the quantum mass. Thus, one of these magnets have optional electromagnetism to direct its field toward any external magnetic field — whether it is a high or weak field. And the magnetic field of the heart is directly proportional to the quantum mass. Therefore, the higher of quantum mass inside the heart, the stronger the magnetic field, and thus leads to the direction of the magnetic field, which compatible with it. This is like a logical debate between the magnets of the heart. And also, the magnetic isomerism of the heart are affected by the presence of an external radio field (e.g., infrasonic) so that the movements of vibrational radio waves work on the distribution of quantum magnetism in a certain direction. For example, one of the magnets distributes a plasmodium arrangement, while other magnets take a correlated ranking and become more solid (hardened). Furthermore, every acoustic coding suitable for cardiac magnetism will affect the genetic characteristics, such as when choosing between two things, that depends on the anterior lobe of the brain due to feedback to give rejection or acceptance. In terms of social relationships, that fall within involuntary commands depend on the heart so when the success of recognition between two hearts, will leads to the formation of a coalition affinity, and if there is a contradiction, will lead to forces of repulsion (disaccord). Therefore, that when the human remains stable on the surface of the Earth other than the surface of the moon, because the disaccord of correlation between their molecules.
In addition, humans are affected by all the environmental events around them, according to visual and auditory interaction (the effect of low frequencies that received by the eye and the auditory nerve). Therefore, any of them will respond to these effects, genetic modifications will occur in their genome, due to the ability of these low frequencies to cause genetic modification, and therefore these genetic modification will then be passed between his offspring as genetic traits, and this is in line with what Darwin's said. But the giraffe's neck length has been pre-integrated to adapt to its environment — it evolved according to emerge of the genetic traits, that previously included in its genome, as adaptive simultaneous to function of time, while showing the periodicity of genetic traits (germplasma), and therefore organism adapted to the environment (future conditions), for survival. Moreover, evolution comes through the emergence of genetic traits in living organisms that synchronically with the function of time — since man began as a giant, they will gradually end up dwarfing. 
As for compulsive effect of physical and sexual characteristics (e.g., masculinity) between males and females according to genetic energy emissions, (through observation for some families), genetic modification are performed through the emission of quantum energy between male and female (which is similar to oxidation-reductase interaction). So suppose that, a woman just as a quantum chromosome donor and a man just as a quantum chromosome acceptor, and vis versa. Moreover, both male and female traits are mutually passed, while man acquires feminine trait, women acquires masculine traits as well.
The energy is exchanged through oxidation-reduction reactions, between physiological traits of male and female according to frequencies encodings, that their influence settles in certain nerve-entanglement and also affects the individual's behavior. As opposed to behavioral influence between males and each other, which plays a directional role in behavior— while the influence between male and female plays an adaptive role in reduction the physical and sexual characteristics of each other (quantitatively). Where these processes depend on the density of quantum charges. Thus, human as a radioactive chemical element, and there is associative affinity (like the co-enzyme), where it plays tuning role in the energy between two bodies, (e.g., between husband and his wife, etc) for the occurrence of an associative reaction, Just as colonization of genetic expression, (quanta-energy encoding), that settles in the one of entanglements.  
In other words, it is impossible to marry a man from a woman, unless the genetic material (in the arms of the isomer structure of their hearts) is identical; to synthesize the field of internal magnetism, as well as to match the angles of entanglement and rotation of rings according to fractal bond, otherwise there will be no coupling, that affinity is responsible for enabling quantum ratios between threads. And these encodings are subject to several processes through the heart, tongue and eye, where they are loaded with a specific audio codec, and structure to match the structure of the receiving end.
Moreover, the forces that are exchanged between two quantum entanglements or two objects remain within the ether.
According to the influence of gravity between two physical objects, so both the passage of time rapidly (time contraction) or the passage of time slowly (time extension) are not merely a phantom feeling, but as a result of actual mobility in reversible and parallel processes of our time, and therefore it proves the multiple universes and at the same time, prove the eligibility of time. In any event, genetics in humans have also been programmed according to the relapse function (decreasing over time). Moreover, the height of the individual (the characteristic of man in the deep past), will gradually decrease (synchronously with time), until it reaches dwarfism. Some of the genetic traits such as height (that have helped to survive and adapt old humans) have been replaced by inherited traits that have contributed to the invention of the machine. Therefore, it is evidence of the periodicity of genetics traits that are synchronized with time, and that the future has been already written. Moreover, the more we advance in the future time towards the end of time (the end of the universe), the more wave encodes that emerged in a particular era of time (e,g., which were in the era of the prophets, as if the past had returned), which will affect human physiology, and urged them to engage in acts that had been practiced in that period of time. Moreover, humanity passes through a pre-programmed plan to match the growth of the universe to its end. Moreover, genetics traits are associated with a quantum percentage of other traits as a result of a certain coding (consisting of an acoustic wavelength, such as the individual's own sound signal) that is accepted through genetic modification, and hence acquired genetic traits emerge. In addition, "Pica" during hunger, such as feeling a desire for something, or being amazed at the beauty of someone may cause the emission of radiation from eyes and heart, that leads to genetic modification in the cell and may lead to a cancerous mutation. These rays have an associative property where they have the ability to pair and modify. This is similar to what happens during pregnancy and when a woman is exposed to pica (craving for some food during pregnancy, etc).  
The sequence of genetic traits from parents to their children as below,

A. The female fetus inherits genetic traits from her father, as following: 
1. His genetic traits which inherited from his father who inherited genetic traits from his father, (father-to-father, and father-to-father, and so on.)
2. His generic traits which inherited from his mother who inherited genetic traits from her father who inherited genetic traits from his mother, and from her father, (mother -to-father and mother-to-father, and so on.) 
And the female fetus is also inherits genetic traits from her mother, as following:
1. Her genetic traits which inherited from her father who inherited genetic traits from his mother who inherited genetic traits from her father, (father-to-mother and father-to-mother, and so on.)
 
B. The male fetus is inherits genetic traits from his mother, as following :
1. Her genetic traits which inherited from her mother, who inherited genetic traits from her mother, (mother-to-mother and mother-to-mother,and so on.)
2. Her genetic characteristics which inherited from her father and who inherited genetic traits traits from his mother, (mother-to-father and  mother-to-father, and so on.)
And the male fetus is also inherits  genetic traits from his father as following:
1. His genetic traits which inherited from his mother who inherited genetic traits from her father (father-to-mother and  father-to-mother, and so on.)
Moreover, the female child resembles his aunt (father's sister) in the genetic traits — while the male child resembles his uncle (mother's brother) in the genetics, and so the gametes came from Adam. Therefore, the fetus inherits the genetic traits of its parents according to a selective genetic sequence. In other words, the sequencing in the transmission of genetic traits is merely a mathematical function that male (masculine traits) its domain, and female (which consists of the genetics traits of the male) its range. Thus, the masculine domain has a range derivative from itself (duality). 
Moreover, the human being came through the processes of evolution (endogeny processes) that began through the evolution of the state of fire material, which evolved into a vital state ("sermatocytes") where a viral property was incorporated in them, and passed through generations, during the inheritance of genetic traits between the offspring. Thus, the human being passes through six evolutionary states to differentiation into the human embryo, where it becomes another creature, so the man is responsible for human reproduction, according to the existence of "EVE" inside the sperm, which merge with the germ cell of women, to form the human embryo. In addition, humans reproduce by asexual reproduction, and therefore the source of the human being is a one object ("monophyletic"). Therefore, we find some traits in humans, which are similar to the endogeny processes such as adaptation, aging and so on, which occur according to the homeostasis process. Thus, mankind came through evolution, starting from a strain of clay (e,g., Silica Sandstone) and then evolved into a sermatocytes, and therefore the determination of the sexual of the fetus, depends on exponential function that mainly on the circadian rhythm, and through which plays a role in creating a suitable ovulatory environment (synchronous interaction occurs between the bio-processes of ovaries and cosmic time) for the germination of the human embryo, as well as in the identification of sexual.

\section{Conclusions}
Since the basis (or base) of the function binds one element of the domain to one element of the range (stable), etc. Therefore, the heart is the nerve basis, which plays a role in the emergence of a vital coupling function, which will lead to the connection of an organism with the humans nerve to control their behavior, directions and desires. In addition, the heart is filled with a special sound frequencies as a quantum charges, that impedes the emergence of a coupling function. When this energy is disintegrated from the heart, a suitable neuronal environment will be formed for the associative organism which will be associated with the nerves of the human, (as linkage organisms) and passes through the heart to the brain, and control the behavior and orientation of human. 
Both the brain and the heart produce specific electrochemical (neurotransmitters) that are associated with specific genetic receptors, that play a role in genetic modification between individuals, according to mutual influence. 
Thus, the associational adhesion affinity is settled in the the nerve cells of the heart and in the surface of the individual, (e.g., nose, skin of hand, eyes and breast) which leading to the stimulation of the reciprocal interaction, where molecules pass from the dominant to the recessif, and thus a genetic modification occurs according to a substitution reaction.
In the human body there are two main stem cells in a semi-perpendicular geometrical position and a specific rhythm, thus every wave rhythm motion corresponds to that position, possibility of genetic modification if and only if the individual accepts that association.
The human return to life after death by germs (which in stem cell or coccyx), where the human contains a solid  totipotent stem cell, when exposed to the water of the synthesis, the emergence of hypha to form the zygote which grew into the previous human, and therefore human just as sporozoite-like organism. 
And the evolution of the human being is as follows:
The clay dynasty then evolved into a sperm which then evolved into a hirudo (which created during phase impaction of morula) and then evolved into a blastocyst (contains ICM or embryoblast) which evolved into bones (that contain a stem cells)  then the flesh, finally differentiated into a fetus. Therefore, both senses of hearing and vision are created from one tissue or from one cell of the human body by endogenous process.
In addition, the logarithm of Eve, with respect to base (Adam's body), is exponent (self) the base, must be raised to produce that Eve. As follows, 
\begin{align}
Adam^{his self) &= Eve\\ And therefore
Self &= log_{Adam}(Eve)\\
\end{align}
The heart is base of self, that plays a role in genetic modification according to an exponential function. Therefore, every idea that a person believes in or is affected by compulsive, it leads to a certain genetic modification that may appear to be phenotypic or behavioral according to exponential function. Moreover the logarithm of Eve and the human offspring respect to the basis of Adam is his self.
Both sperm of the man and the woman, have a different genetic charge which multiplied by an exponential function. Therefore, which sperm are placed in exponent, they control the sexual of the fetus, where a multiplication of the base charge (oocytes), occurs to produce the quantum charge of the male fetus. Furthermore, the male fetus carries a different genetic charge than that of the female fetus. That means the logarithm of a sexual fetus is the exponent to which another sperm, the base must be raised to determines the sexual of the fetus as follows,
\begin{align} 
Male fetus &= oocytes^{sperm}\\ for that, 
Sperm's self &= log_{oocytes}(male fetus)\\
\end{align}
Where the physical cells of the fetus are inherited from those sperm at the bottom (base), while determining the sexual of the fetus is the responsibility of the sperm that floated (exponent). In addition, both somatic and sexual cells have been merged into a solid stem cell, and therefore the human comes back to life after he die if conditions of biological germination are met.
In other words, the logarithm of determining the sexual of the fetus depends on which sperm is less dense than the other, during the integration of both male and female sperm-water according to exponential function, and therefore every person has a half-life, according to the exponential decay.
Process of evolution as follows,
\begin{align}
Adam^{his self} &= Eve\\ , then the logarithm of self with respect to base Adam is Eve, as follows,
\begin{align}
Self &= log_{Adam} (Eve)\\
\end{align}
And the process of offspring as follows, 
\begin{align}
Eve^{Adam} &= offspring\\, and the logarithm of Adam, with respect to base (Eve), is their offspring, the base, must be raised to produce that offspring.
Adam &= log_{Eve} (offspring)\\
\end{align}
As for the base (female) respect to its exponent (the self of male which stored in Adam), while the base (male) respect to its exponent (the female) such as Eve who came by budding, and therefore both male and female have sperm water, which play a role in determining the sexual of the fetus, according to the reverse function (logarithm), and so on. Therefore, if the female sperm at the base, the fetus will be male, or if the sperm of the male at the base, the fetus will be female.
Moreover, the determination of the sexual of the fetus occurs according to a specific exponential function on which sperm is placed in the exponent. If the sperm of the male is the base, the exponent is the female sperm, and therefore the fetus is a female resulting from the self of her father, and this girl acquires traits from her father more than that acquired by her mother, as follows,
\begin{align}
female fetus &= father's sperm^{mother's sperm}\\
\end{align} thus the logarithm of female fetus respect to base sperm is Oocytes, due to budding process. 
\begin{align}
Male fetus &= mother's sperm^{father's sperm}\\
\end{align}
Thus, the male fetus inherits genetic traits from his mother (which she inherited from her father) rather than from his father. Moreover, a man marries only the woman who serves as a complimentary, who has been previously prepared.
Moreover, both Eve and offspring of human were then created from one source of self that was introduced into Adam's body. Therefore, the self has been integrated into the sperm and inherited by successive generations, and to ensure reproduction. The formation of the fetus passes through an integrative equation, where it starts from the charge of one sperm until it is integrated (at a certain point) by exponential multiplication of the other sperm, until it becomes an embryo. When the natural selection is different, individuals have more features than others, such as in the scientific side, and other issues that are useful for survival and adaptation.
 \end{document}   
